
# Simulation

## Data

```{r simulation_data, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Code generating the data used in the case, possibly with some randomness.

q1_table_to_fill <- tibble::tibble(x = base::character(2), y = base::numeric(2))
q1_table_with_solution <- tibble::tibble(x = c("A","B"), y = c("22","23"))

```

## Files

```{r simulation_files, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Code generating the data used in the case, possibly with some randomness.
files <- base::list(
  q1_table_with_solution
)
```










# Part 1

A case is organized in parts. Each part has its own case description and series of questions. When the case is created, each part will be a distinct PDF (+ CSV or excel for data if requested) file or a distinct tab in the shiny dashboard, depending on the desired output.  



## Description

Write here in rmarkdown syntax the case with all the data deemed necessary. This case description will be displayed for all the questions in the corresponding section.  





## Questions





### Question 1

#### Interrogation

```{r question_1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
question_1 = base::list(
  interrogation = 'Write here the question asked to the student.',
  type = "computation",
  correct = (labor_administrative+administrative_rent),
  documents = base::character(1),
  hints = base::list(
    'Did you check this?',
    'Did you do that?'
  )
)
```

#### Solution

Write here in rmarkdown syntax the complete solution to the question.





### Question 2

#### Interrogation

```{r question_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
question_2 = base::list(
  interrogation = 'Write here the question asked to the student.',
  type = "table",
  table = q1_table_to_fill,
  readonly = c(1),
  shaderow = c(5),
  height = 200,
  correct = q1_table_with_solution,
  documents = base::character(1),
  hints = base::list(
    'Did you check this?',
    'Did you do that?'
  )
)
```

#### Solution

Write here the complete solution to the question.





### Question 3

#### Interrogation

```{r question_3, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
question_3 = base::list(
  interrogation = 'Write here the question asked to the student.',
  type = "words",
  correct = c("joint","split-off","separable"),
  documents = base::character(1),
  hints = base::list(
    'Did you check this?',
    'Did you do that?'
  )
)
```

#### Solution

Write here the complete solution to the question.





### Question 4

#### Interrogation

```{r question_4, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
question_4 = base::list(
  interrogation = 'Write here the question asked to the student.',
  type = "keywords",
  correct = c("pattern in regex"),
  documents = base::character(1),
  hints = base::list(
    'Did you check this?',
    'Did you do that?'
  )
)
```

#### Solution

Write here the complete solution to the question.





Meta-information
================
exextra[title]:Title of the case.  
exextra[type]:Case  
exextra[document]:CXXXXXXXXX  
exextra[tag_custom]:  
