---
title: Feedback on your repair of the fifth quiz.
output: html_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)

group_size <- base::round(base::length(grades$grade),2)
group_median <- base::round(stats::median(grades$grade),2)
group_mean <- base::round(base::mean(grades$grade),2)
group_sttdev <- base::round(stats::sd(grades$grade),2)

firstname <-  dplyr::filter(students, student == studentid)$firstname[[1]]
student_grade <- dplyr::filter(grades, student == studentid)
student_grade <- student_grade$grade[1]

thresholds <- c(0,6,8,10)
comments <- c(
    "I am sorry, this is not very good overall. I hope the feedback below will help you understand what you did wrong.",
    "This is fine, although less than most of the other students who participated. I hope the feedback below will help you understand what you did wrong.",
    "this is very good! There is not much to improve, and the feedback below may help you identify what.",
    "This is excellent!"
)
adapted_comment <- teachR::reports_customize_comment(student_grade, thresholds, comments)
```


Dear `r firstname`,

I hope you are well. Please find in this e-mail an individual feedback about the repair of the fifth quiz in Management Accounting for Business and Economics. Your total grade was **`r student_grade`** out of 10. `r adapted_comment`  

I wish you an excellent week,

Dr. Nicolas Mangin  

<hr>

`r group_size` students participated to this quiz.  The median is `r group_median`, the average is `r group_mean`, and the standard deviation is `r group_sttdev`.  

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.align="center"}
teachR::reports_draw_grade_density(grades, studentid)
```

Please find in the following table a detailed individual feedback about your answers. The first three columns indicate the version of the question you had to answer, the question asked, and the number of points associated to that question. Then you ca see the answer you selected, whether it is right or wong, the success rate on that item, and the points you earned. Note that since there is no partial credits, either you earned all the points associated to a specific question or you eanr none. After this, you can find an explanation and a link to the section of the onmine textbook addressing this point.  


```{r echo=FALSE}
teachR::reports_feedback_on_closed(feedback, studentid)
```

