


**Add a quote and citations.**

> This is a quote.

You can insert citations in the text [@Mangin2022].


**Add a mathematical formula**

You can insert Latex formulas in in text like this $Y = \beta_0 + \beta_1 X^2$ and as a bloc like this:

$$
\begin{aligned}
0 & = Q_B \times (P-UVC) - FC \\
Q_B \times (P-UVC) & = FC \\
Q_B & = \frac{FC}{P-UVC}
\end{aligned}
$$
[Here is a list of mathematical expressions](https://oeis.org/wiki/List_of_LaTeX_mathematical_symbols) that you can use to write these formulas.  


**Add a table**

```{r table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(kableExtra)
library(ggplot2)
table <- diamonds |>
  dplyr::slice_head(n = 10)

table |>
  kableExtra::kbl(format = "html", digits = 2, align = "lllcrrrrrr") |>
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = FALSE,
    font_size = 12,
    position = "center"
  ) |>
  kableExtra::column_spec(
    7, color = "white",
    background = kableExtra::spec_color(table$price, end = 0.7),
    popover = base::paste("price:", table$cut)
  )
```

[Here is a webpage explaining how you can customize your tables](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html) with KabelExtra.  


**Add an exercise with a collapsible solution**

<div class="exercise">

**Exercise.** You can write within this "div" the core of the exercise. 

</div>

<section class="solution"><input type="checkbox" name="collapse1" id="handle1"><h2 class="handle"><label for="handle1">
**Solution.** *Try to answer and then click on this colored area to reveal the solution.* 
</label></h2><div class="hiddencontent">

Here you can write the solution for the exercise which will only be displayed if the student clicks on it. Note that if you have more than one exercise on the same page, you will have to increment the name and id above.  

</div></section>



**Add a diagram**

```{r diagram, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, out.width='100%'}
library(DiagrammeR)
diagram <- DiagrammeR::create_graph() |>
  
  DiagrammeR::add_node(label = "Cause", node_aes = DiagrammeR::node_aes(shape = "rectangle", color = "black", fontcolor = "white", fillcolor = "grey20", fontsize = 12, x = 0, y = 0, penwidth = 1, width = 1.5, height = 0.5)) |> #1
  
  DiagrammeR::add_node(label = "Mediator", node_aes = DiagrammeR::node_aes(shape = "rectangle", color = "black", fontcolor = "white", fillcolor = "grey20", fontsize = 12, x = 2, y = 0, penwidth = 1, width = 1.5, height = 0.5)) |> #2
  
  DiagrammeR::add_node(node_aes = node_aes(shape = "rectangle", color = "black", fontcolor = "black", fillcolor = "black", fontsize = 0, x = 3, y = 0, penwidth = 0, width = 0, height = 0)) |>
  
  DiagrammeR::add_node(label = "Consequence", node_aes = DiagrammeR::node_aes(shape = "rectangle", color = "black", fontcolor = "white", fillcolor = "grey20", fontsize = 12, x = 4, y = 0, penwidth = 1, width = 1.5, height = 0.5)) |> #3
  
  DiagrammeR::add_node(label = "Moderator", node_aes = DiagrammeR::node_aes(shape = "rectangle", color = "black", fontcolor = "white", fillcolor = "grey20", fontsize = 12, x = 3, y = 1, penwidth = 1, width = 1.5, height = 0.5)) |> #4
  
  DiagrammeR::add_edge(from = 1, to = 2, edge_aes = DiagrammeR::edge_aes(style = "solid", color = "black", fontcolor = "black", fontsize = 10, penwidth = 2, arrowhead = "normal")) |>
  
  DiagrammeR::add_edge(from = 2, to = 3, edge_aes = DiagrammeR::edge_aes(style = "solid", color = "black", fontcolor = "black", fontsize = 10, penwidth = 2, arrowhead = "none")) |>
  
  DiagrammeR::add_edge(from = 3, to = 4, edge_aes = DiagrammeR::edge_aes(style = "solid", color = "black", fontcolor = "black", fontsize = 10, penwidth = 2, arrowhead = "normal")) |>
  
  DiagrammeR::add_edge(from = 5, to = 3, edge_aes = DiagrammeR::edge_aes(style = "solid", color = "black", fontcolor = "black", fontsize = 10, penwidth = 2, arrowhead = "normal"))

DiagrammeR::render_graph(diagram)
```

[Here is a webpage explaining how you can customize your diagrams](https://rich-iannone.github.io/DiagrammeR/graphviz_and_mermaid.html) with DiagrammeR.  


**Add a graph**

```{r graph, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(ggplot2)
diamonds |>
  dplyr::slice_sample(n = 500) |>
  ggplot(aes(x=carat, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", formula = "y ~ x")
```


**Add an image**

![](https://images.unsplash.com/photo-1644018335954-ab54c83e007f?ixlib=rb-1.2.1&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=1170&q=80){width=80%}


**Add a video**

```{r video, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
teachR::add_video(vid = "gM95HHI4gLk", host = "Youtube")
```


**Add a star rating**

```{r starrating, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
teachR::add_rating(sourcename = "SOURCE_NAME", filename = "FILE_NAME")
```


**Add a form for written comments**

```{r comment, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
teachR::add_comment(sourcename = "SOURCE_NAME", filename = "FILE_NAME")
```


**References**


Meta-information
================
exextra[title]:Title of the page.  
exextra[type]:Page  
exextra[document]:PXXXXXXXXX  
exextra[tag_authors]: Dr. Nicolas Mangin  
