```{r preparation, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
versionid <- "QXXXXXXXXX_US.Rmd"
prm <- teachR::questions_set_parameters(versionid, test_parameters, as_latex, record_version)
base::set.seed(prm$seed)

exercise <- teachR::questions_create_two_statements(
  feedbacks = feedbacks,
  documents = "DXXXXXXXXX",
  langiso = "US"
)
prepanswerlist <- exercise |>
  dplyr::select(letter, correct) |>
  dplyr::group_by(letter) |>
  dplyr::summarise(correct = base::min(correct))
```



Question
========
`r prm$show_version` Consider the two following statements:  

(1) *`r exercise$proposition[[1]]`*  

(2) *`r exercise$proposition[[2]]`*  

Which of the following answers is correct? `r prm$show_points`

```{r question, echo = FALSE, results = "asis"}
exams::answerlist(c(
  "Both statements are false.",
  "Statement (1) is true, but statement (2) is false.",
  "Statement (1) is false, but statement (2) is true.",
  "Both statements are true."
), markup = "markdown")
```



Solution
========

`r exercise$explanation[1]` Therefore, statement (1) is `r if (exercise$value[1] == 1) "true." else "false."`  

`r exercise$explanation[2]` Therefore, statement (2) is `r if (exercise$value[2] == 1) "true." else "false."`

```{r solution, echo = FALSE, results = "asis"}
teachR::questions_record_version(prm$record_version, prm$test, versionid, exercise)
exams::answerlist(ifelse(
    prepanswerlist$correct,
    "This answer is correct.",
    "This answer is incorrect."
), markup = "markdown")
```



Meta-information
================
exname: `r versionid`  
extype: schoice  
exsolution: `r exams::mchoice2string(prepanswerlist$correct, single = TRUE)`  
exextra[title]:Title of the question.  
exextra[type]:Statements  
exextra[document]:  
exextra[tag_custom]:  
